Your main manuscript title

### 2021-06-16 forecast/paper/supplement.tex
Edits thru discussion
- Left parts C and D of results blank, until Dan gets figures
- Discussion still needs to be fleshed out
- Figs 1 and 2 still need to be replaced by their real versions

\input{forecast-prelim.tex}

@@

@@

\begin{figure}
\centering
\includegraphics[width=\textwidth]{frog}
\caption{Second figure}
\end{figure}

@@

@@

\bibliography{pnas-sample}

>>>>

\input{../../common/prelim.tex}

\providecommand{\tightlist}{%
  \setlength{\itemsep}{0pt}\setlength{\parskip}{0pt}}

@@

\section*{PNAS Template material, to be removed}

@@

\begin{figure}
\centering
\includegraphics[width=\textwidth]{pnas-materials/frog}
\caption{Second figure}
\end{figure}

@@

\clearpage

\hypertarget{figures-from-results}{%
\section{Figures from results}\label{figures-from-results}}

\hypertarget{forecasts}{%
\subsection{Forecasts}\label{forecasts}}

\begin{center}\includegraphics[width=\linewidth]{fig/fcast-1} \end{center}

\begin{center}\includegraphics[width=\linewidth]{fig/fcast-finalized-1} \end{center}

\begin{center}\includegraphics[width=\linewidth]{fig/fcast-honest-v-finalized-1} \end{center}

\begin{center}\includegraphics[width=\linewidth]{fig/fcast-adjusted-1} \end{center}

\begin{center}\includegraphics[width=\linewidth]{fig/wis-densities-1} \end{center}

\hypertarget{all-periods}{%
\subsubsection{All periods}\label{all-periods}}

\begin{center}\includegraphics[width=\linewidth]{fig/fcast-alldates-1} \end{center}

\begin{center}\includegraphics[width=\linewidth]{fig/fcast-alldates-adjusted-1} \end{center}

\hypertarget{only-gs-locations}{%
\subsubsection{Only GS locations}\label{only-gs-locations}}

\begin{center}\includegraphics[width=\linewidth]{fig/fcast-gs-locations-1} \end{center}

\begin{center}\includegraphics[width=\linewidth]{fig/fcast-gs-locations-adjusted-1} \end{center}

\hypertarget{trajectories-deprecated}{%
\subsection{Trajectories (deprecated)}\label{trajectories-deprecated}}

\hypertarget{hotspots}{%
\subsection{Hotspots}\label{hotspots}}

\begin{center}\includegraphics[width=\linewidth]{fig/hot-1} \end{center}

\begin{center}\includegraphics[width=\linewidth]{fig/hot-finalized-1} \end{center}

\begin{center}\includegraphics[width=\linewidth]{fig/hot-honest-v-finalized-1} \end{center}

\hypertarget{all-periods-1}{%
\subsubsection{All periods}\label{all-periods-1}}

\begin{center}\includegraphics[width=\linewidth]{fig/hot-alldates-1} \end{center}

\hypertarget{only-gs-locations-1}{%
\subsubsection{Only GS locations}\label{only-gs-locations-1}}

\begin{center}\includegraphics[width=\linewidth]{fig/hot-gs-locations-1} \end{center}

\hypertarget{figure-5}{%
\subsubsection{Figure 5}\label{figure-5}}

\begin{itemize}
\tightlist
\item
  Currently, this is the ``main'' figure. WIS and hotspots, 2 panels,
  only 2020, honest training.
\end{itemize}

\begin{center}\includegraphics[width=\linewidth]{fig/figure5-1} \end{center}

\hypertarget{figure-6-misleading-retrospective-analysis}{%
\subsubsection{Figure 6 (misleading retrospective
analysis)}\label{figure-6-misleading-retrospective-analysis}}

\begin{itemize}
\tightlist
\item
  WIS and hotspots, 2 panels, only 2020, honest training.
\end{itemize}

\begin{center}\includegraphics[width=\linewidth]{fig/figure6-1} \end{center}

\hypertarget{correlations-with-lagged-actuals}{%
\subsection{Correlations with lagged
actuals}\label{correlations-with-lagged-actuals}}

\begin{center}\includegraphics[width=\linewidth]{fig/cor-wis-ratio-1} \end{center}

\begin{center}\includegraphics[width=\linewidth]{fig/cor-wis-ratio-m1-1} \end{center}

\hypertarget{upswings-vs-downswings}{%
\subsection{Upswings vs downswings}\label{upswings-vs-downswings}}

\begin{center}\includegraphics[width=\linewidth]{fig/upswing-histogram-1} \end{center}

\begin{center}\includegraphics[width=\linewidth]{fig/upswing-histogram-logged-1} \end{center}

\begin{tabular}[t]{lrrrrr}
\toprule
udf & CHNG-CLI & CHNG-COV & CTIS-CLIIC & DV-CLI & Google-AA\\
\midrule
down & 0.79 & 0.80 & 0.83 & 0.81 & 0.81\\
flat & 0.12 & 0.17 & 0.28 & 0.18 & 0.17\\
up & -0.57 & -0.56 & -0.53 & -0.53 & -0.47\\
\bottomrule
\end{tabular}

\hypertarget{leadingness-and-laggingness}{%
\subsection{Leadingness and
laggingness}\label{leadingness-and-laggingness}}

\begin{center}\includegraphics[width=\linewidth]{fig/leading-and-lagging-1} \end{center}

\begin{center}\includegraphics[width=\linewidth]{fig/diff-in-lead-lag-1} \end{center}

\hypertarget{side-figures-in-their-own-scripts}{%
\section{Side figures (in their own
scripts)}\label{side-figures-in-their-own-scripts}}

\begin{center}\includegraphics[width=\linewidth]{fig/ccf-dv-finalized-1} \end{center}

\begin{center}\includegraphics[width=\linewidth]{fig/ny-trajectory-1} \end{center}

\begin{center}\includegraphics[width=\linewidth]{fig/revisions-dv-jhu-1} \end{center}

@@

\bibliography{../../common/covidcast.bib,pnas-materials/pnas-sample.bib}
